Sound and Automated Synthesis of Digital Controllers for Continuous Plants

### 2017-03-13 slides/presentation.tex
pres

$$
M=\left( 
\begin{array}{ccc}
v^{(0)}_{1} &\cdots & v^{(0)}_{N_S}\\
v^{(1)}_{1} &\cdots&  v^{(1)}_{N_S}\\
\vdots&\vdots&\vdots\\
v^{(N_S-1)}_{1} &\cdots&  v^{(N_S-1)}_{N_S}\\
\end{array}
\right), $$
%
$$
v_{j}^{(k)}=\left\{
\begin{array}{ll}
c_{j-1}, & k=0\\
0,&k>0 \wedge \mbox{if}~j>N_S-k\\
v_{1}^{(k-1)}-v_{N_S-j}^{(k-1)} . \frac{v_{1}^{(k-1)}}{v_{N_S-k}^{(k-1)}}, &k>0 \wedge  \mbox{if}~j\leq N_S-k\\
\end{array}
\right.
$$
%
$S(z)$ is stable $\Leftrightarrow$
$$
%\phi_\mathit{stability} \equiv 
\textcolor{blue}{S(1) > 0}\ \uncover<2->{\wedge\ \textcolor{blue}{(-1)^{N_S} S(-1) > 0}}\ \uncover<3->{\wedge\ \textcolor{blue}{|c_0| < c_{N_S}}}\ \uncover<4>{\wedge\ \textcolor{blue}{\forall k, v_1^{(k)} > 0}}
$$

@@

%
\begin{frame}{Our Objective}

@@

@@

%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Illustrative Example} \label{sec:running-ex}
%
%We illustrate our approach with a classical cruise control example from the
%literature~\cite{Astrom08}.  It highlights the challenges that
%arise when using finite-precision arithmetic in digital control.  We are
%given a discrete plant model (with a time step of $0.2$\,s), 
%represented by the following $z$-expression:
%%
%\begin{equation}
%\label{Eq:running-example-plant}
%G(z) = \frac{0.0264}{z-0.9998}.
%\end{equation}
%
%Using an optimization tool, the authors
%of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
%controller for this plant, which is characterized by the following
%$z$-domain transfer function:
%%
%\begin{equation}
%\label{Eq:running-example-controller}
%C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
%\end{equation}
%%
%The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that the controller
%$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the closed-loop
%system for the discrete plant model $G(z)$
%in~\eqref{Eq:running-example-plant}.  However, if the effects of
%finite-precision arithmetic are considered, then this closed-loop system
%becomes unstable.
%%
%For instance, an implementation of $C(z)$ using 
%$\mathbb R \param {4}{16}$ fixed-point
%numbers (i.e., $4$ bits for the integer part and $16$ bits for the
%fractional part) can be modeled as: 
%%
%\begin{equation}
%\label{Eq:running-example-controller-quantized}
%\resizebox{.47\textwidth}{!}{
%$\tilde{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
%{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
%}
%\end{equation} 
%%
%The resulting system, 
%%using the typical series loop configuration, 
%where $\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
%Notice that this is disregarding further approximation effects on the plant caused by quantization in the verifier (i.e., $\tilde{G}(z)$).
%%\aabatecmt{[hang in there - did we not consider FWL on $G(z)$? why not?]}
%%\dariocmt{we are explaining the case where a real plant (no FWL) is not correctly stabilized by $\tilde{C}$, so although our analysis might evaluate $\tilde{G}(z)$, the problem statement is over $G(z)$}
%Figure~\ref{fig:original} gives the Bode diagram for the digital controller
%represented in~\eqref{Eq:running-example-controller}: 
%as the phase margin is negative, 
%the controller is unstable when considering the FWL effects.
%
%
\begin{frame}[fragile]{Step Response for the Candidate Solutions}
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step0.pdf}
        \caption{Original controller}
        \label{fig:step0}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step1.pdf}
        \caption{First solution by \tool}
        \label{fig:step1}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step2.pdf}
        \caption{Final solution by \tool}
        \label{fig:step2}
    \end{subfigure}
\end{figure}
The Original Controller was synthesised ignoring FWL effects and as can be seen, it becomes unstable over time.
\end{frame}
%
\begin{frame}[fragile]{Synthesised Results}
\begin{figure}
 \begin{tikzpicture}
\begin{axis}[ylabel=order,xlabel=time,xmode=log
]
\addplot[scatter,only marks,mark=*] table{./results.dat};
\end{axis}
\end{tikzpicture}
\end{figure}
\end{frame}

\begin{frame}[fragile]{Synthesised Results}

>>>>

$$
M=\left( 
\begin{array}{ccc}
v^{(0)}_{1} &\cdots & v^{(0)}_{N_S}\\
v^{(1)}_{1} &\cdots&  v^{(1)}_{N_S}\\
\vdots&\vdots&\vdots\\
v^{(N_S-1)}_{1} &\cdots&  v^{(N_S-1)}_{N_S}\\
\end{array}
\right), $$
%
$$
v_{j}^{(k)}=\left\{
\begin{array}{ll}
c_{j-1}, & k=0\\
0,&k>0 \wedge \mbox{if}~j>N_S-k\\
v_{1}^{(k-1)}-v_{N_S-j}^{(k-1)} . \frac{v_{1}^{(k-1)}}{v_{N_S-k}^{(k-1)}}, &k>0 \wedge  \mbox{if}~j\leq N_S-k\\
\end{array}
\right.
$$
%
\begin{eqnarray*}
&S(z) \text{ is stable } \Leftrightarrow& \\ 
%\phi_\mathit{stability} \equiv 
&\textcolor{blue}{S(1) > 0}\ \uncover<2->{\wedge\ \textcolor{blue}{(-1)^{N_S} S(-1) > 0}}\ \uncover<3->{\wedge\ \textcolor{blue}{|c_0| < c_{N_S}}}\ \uncover<4>{\wedge\ \textcolor{blue}{\forall k, v_1^{(k)} > 0}}&
\end{eqnarray*}

@@

%
\begin{frame}{Objective}

@@

\textcolor{red}{Copy here CEGIS architecture scheme.}

\begin{frame}{Case Study}

\textcolor{red}{Introduce details of case study. }

@@

%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Illustrative Example} \label{sec:running-ex}
%
%We illustrate our approach with a classical cruise control example from the
%literature~\cite{Astrom08}.  It highlights the challenges that
%arise when using finite-precision arithmetic in digital control.  We are
%given a discrete plant model (with a time step of $0.2$\,s), 
%represented by the following $z$-expression:
%%
%\begin{equation}
%\label{Eq:running-example-plant}
%G(z) = \frac{0.0264}{z-0.9998}.
%\end{equation}
%
%Using an optimization tool, the authors
%of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
%controller for this plant, which is characterized by the following
%$z$-domain transfer function:
%%
%\begin{equation}
%\label{Eq:running-example-controller}
%C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
%\end{equation}
%%
%The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that the controller
%$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the closed-loop
%system for the discrete plant model $G(z)$
%in~\eqref{Eq:running-example-plant}.  However, if the effects of
%finite-precision arithmetic are considered, then this closed-loop system
%becomes unstable.
%%
%For instance, an implementation of $C(z)$ using 
%$\mathbb R \param {4}{16}$ fixed-point
%numbers (i.e., $4$ bits for the integer part and $16$ bits for the
%fractional part) can be modeled as: 
%%
%\begin{equation}
%\label{Eq:running-example-controller-quantized}
%\resizebox{.47\textwidth}{!}{
%$\tilde{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
%{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
%}
%\end{equation} 
%%
%The resulting system, 
%%using the typical series loop configuration, 
%where $\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
%Notice that this is disregarding further approximation effects on the plant caused by quantization in the verifier (i.e., $\tilde{G}(z)$).
%%\aabatecmt{[hang in there - did we not consider FWL on $G(z)$? why not?]}
%%\dariocmt{we are explaining the case where a real plant (no FWL) is not correctly stabilized by $\tilde{C}$, so although our analysis might evaluate $\tilde{G}(z)$, the problem statement is over $G(z)$}
%Figure~\ref{fig:original} gives the Bode diagram for the digital controller
%represented in~\eqref{Eq:running-example-controller}: 
%as the phase margin is negative, 
%the controller is unstable when considering the FWL effects.

\begin{frame}[fragile]{Outcomes: Step Response}
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step0.pdf}
        \caption{Original\\ controller}
        \label{fig:step0}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step1.pdf}
        \caption{Controller (first step)}
        \label{fig:step1}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step2.pdf}
        \caption{Controller (final step)}
        \label{fig:step2}
    \end{subfigure}
\end{figure}

\begin{itemize} 
\item 
original controller was synthesised ignoring FWL effects (becomes unstable over time) 
\end{itemize}

\begin{frame}[fragile]{Outcomes: Controller Order}
\begin{figure}
 \begin{tikzpicture}
\begin{axis}[ylabel=order,xlabel=time,xmode=log
]
\addplot[scatter,only marks,mark=*] table{./results.dat};
\end{axis}
\end{tikzpicture}
\end{figure}
\end{frame}

\begin{frame}[fragile]{Outcomes: Benchmark}
